\Large \bf Cyclone: High Availability for Persistent Key Value Stores

### 2017-08-09 paper/paper.tex
Updates.

\thispagestyle{empty}

\begin{abstract}
\vspace{0.1in}
Persistent key value stores are an important component of many distributed data
serving solutions with innovations targeted at taking advantage of growing flash
speeds. Unfortunately their performance is hampered by the need to maintain and
replicate a write ahead log to guarantee availability in the face of machine and
storage failures. Cyclone is a replicated log plug-in for key value stores that
systematically addresses various sources of this bottleneck. It uses a small
amount of non-volatile memory directly addressable by the CPU - such as in the
form of NVDIMMs or Intel 3DXPoint - to remove block oriented IO devices such as
SSDs from the critical path for appending to the log. It then addresses network
overheads using an implementation of the RAFT consensus protocol that is
designed around a userspace network stack to relieve the CPU of the burden of
data copies. Finally, it provides a way to efficiently map the commutativity in
key-value store APIs to the parallelism available in commodity NICs via multiple
transmit receive queues to scale replication performance on multicore
machines. Cyclone is able to replicate millions of small updates per second
using only commodity 10 gigabit ethernet adapters. As a practical application,
we use it to improve the performance (and availability) of RocksDB, a popular
persistent key value store by an order of magnitude when compared to its own
write ahead log without replication.
\end{abstract}

@@

The core network operation in replication is to receive a request from the
client at the leader replica and send that exact same request (as a log entry)
to all follower replicas. The leader therefore \emph{multicasts} a received
request packet to follower replicas, a problem well studied in the networking
community when building software packet switches. Software packet switches reach
impressive speeds of millions of packets forwarded per second~\cite{dpdk_perf}, 
a number far in excess of the few hundreds of packets we manage in
Figure~\ref{fig:problem}. The key insight in removing network overheads in
Cyclone is therefore to approximate a software packet switch for the networking
component of Cyclone. We do this by implementing Cyclone's network stack on top
of the Data Plane Development Kit (DPDK)~\cite{dpdk}, that provides low latency
userspace access to an ethernet NIC. We discuss Cyclone's network protocol in
Section~\ref{sec:netprot}. There are two key challenges in implementing a
consensus protocol as a software packet switch.

>>>>

%\thispagestyle{empty}

\begin{abstract}
\vspace{0.05in}
Persistent key value stores are an important component of many distributed data
serving solutions with innovations targeted at taking advantage of growing flash
speeds. Unfortunately their performance is hampered by the need to maintain and
replicate a write ahead log to guarantee availability in the face of machine and
storage failures. Cyclone is a replicated log plug-in for key value stores that
systematically addresses various sources of this bottleneck. It uses a small
amount of non-volatile memory directly addressable by the CPU - such as in the
form of NVDIMMs or Intel 3DXPoint - to remove block oriented IO devices such as
SSDs from the critical path for appending to the log. It then addresses network
overheads using an implementation of the RAFT consensus protocol that is
designed around a userspace network stack to relieve the CPU of the burden of
data copies. Finally, it provides a way to efficiently map the commutativity in
key-value store APIs to the parallelism available in commodity NICs.
Cyclone is able to replicate millions of small updates per second
using only commodity 10 gigabit ethernet adapters. As a practical application,
we use it to improve the performance (and availability) of RocksDB, a popular
persistent key value store by an order of magnitude when compared to its own
write ahead log without replication.
\end{abstract}

@@

The core network operation in replication is to receive a request from the
client at the leader replica and send that exact same request (as a log entry)
to all follower replicas. The leader therefore \emph{multicasts} a received
request packet to follower replicas, a problem well studied in the networking
community when building software packet switches. Software packet switches reach
impressive speeds of millions of packets forwarded per second~\cite{dpdk_perf}, 
a number far in excess of the few thousands of packets we manage in
Figure~\ref{fig:problem}. The key insight in removing network overheads in
Cyclone is therefore to approximate a software packet switch for the networking
component of Cyclone. We do this by implementing Cyclone's network stack on top
of the Data Plane Development Kit (DPDK)~\cite{dpdk}, that provides low latency
userspace access to an ethernet NIC. We discuss Cyclone's network protocol in
Section~\ref{sec:netprot}. There are two key challenges in implementing a
consensus protocol as a software packet switch.
